Developing a preprint culture in biology

### 2012-10-30 ms.tex
fix refs
fix typo in Ethan's address

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{Developing a preprint culture in biology}
}
% Insert Author names, affiliations and corresponding author email.
\\
Philippe Desjardins-Proulx$^{1, 2,\ast}$, 
Ethan P. White$^{3}$, 
Joel J. Adamson$^{4}$,
Karthik Ram$^{5}$,
Timoth\'ee Poisot$^{1,2,6}$,
Dominique Gravel$^{1,2}$
\\
\bf{1} Theoretical Ecosystem Ecology laboratory, Universit\'e du Qu\'ebec \`a Rimouski, Quebec, Canada.
\\
\bf{2} Quebec Center for Biodiversity Science, McGill University, Quebec, Canada.
\\
\bf{3} Departement of Bology, Utah State University, Utah, United-States of America.
\\
\bf{4} Ecology, Evolution and Organismic Biology, University of North Carolina at Chapel Hill, North Carolina, United-States of America
\\
\bf{5} Environmental Science, Policy, and Management. University of California, Berkeley, California, United-States of America.
\\
\bf{6} International Network for Next-Generation Ecology.
\\
$\ast$ E-mail: philippe.d.proulx@gmail.com
\end{flushleft}

@@

PDP is supported by an Alexander Graham Bell scholarship from the National
Sciences and Engineering Council of Canada. EPW is supported by a CAREER Award
from the National Science Foundation (DEB-0953694). JJA is supported by NSF
DEB-0614166 and NSF DEB-0919018.  TP is supported by a FQRNT-MELS post-doctoral
scholarship. KR is supported by NSF DEB-1021553. DG is funded by a Discovery
Grand from the National Sciences and Engineering Council of Canada and by the
Canada Research Chair program.

>>>>

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{Developing a preprint culture in biology}
}
% Insert Author names, affiliations and corresponding author email.
\\
Philippe Desjardins-Proulx$^{1, 2,\ast}$, 
Ethan P. White$^{3}$, 
Joel J. Adamson$^{4}$,
Karthik Ram$^{5}$,
Timoth\'ee Poisot$^{1,2,6}$,
Dominique Gravel$^{1,2}$
\\
\bf{1} Theoretical Ecosystem Ecology laboratory, Universit\'e du Qu\'ebec \`a Rimouski, Quebec, Canada.
\\
\bf{2} Quebec Center for Biodiversity Science, McGill University, Quebec, Canada.
\\
\bf{3} Departement of Biology, Utah State University, Utah, United-States of America.
\\
\bf{4} Ecology, Evolution and Organismic Biology, University of North Carolina at Chapel Hill, North Carolina, United-States of America
\\
\bf{5} Environmental Science, Policy, and Management. University of California, Berkeley, California, United-States of America.
\\
\bf{6} International Network for Next-Generation Ecology.
\\
$\ast$ E-mail: philippe.d.proulx@gmail.com
\end{flushleft}

@@

PDP is supported by an Alexander Graham Bell scholarship from the National
Sciences and Engineering Council of Canada. EPW is supported by a CAREER Award
from the National Science Foundation (DEB-0953694). JJA is supported by NSF
DEB-0614166 and NSF DEB-0919018.  TP is supported by a FQRNT-MELS post-doctoral
scholarship. KR is supported by NSF DEB-1021553. DG is funded by a Discovery
Grant from the National Sciences and Engineering Council of Canada and by the
Canada Research Chair program.
